HealpixNet: Efficient spherical Convolutional Neural Network with Healpix sampling for cosmological applications

### 2018-07-02 scnn.tex
update appendix + results

\subsection{Interpretation}
\assign{Nathanaël, Tomek, Michaël}

Show the learned filters and feature maps and try to interpret them.
\todo{\\ TK and NP: Figure of filters from the mass map clasification}

@@

\section{Spherical harmonics VS graph Fourier eigenvectors}
\figref{g:graph_harmonics} displays the first 16 eigenvectors of the
graph Fourier basis used for the convolution. While their is a clear
resemblance with the spherical harmonic, the small irregularities in the
sampling (see \figref{healpix_graph_4}) have two important effects on the
graph Fourier eigenvectors.  First, some graph eigenvectors will be
localized~\cite{perraudin2018global}, i.e: they will span only a small subpart
of the sphere.  Second, as Nside increase toward infinity and hence the number
of pixel $n\rightarrow \infty$, we are still unsure if the graph eigenvectors
converge toward the spherical harmonics. We believe that it might be the case
for a different graph construction (fully connected) and that a proof could be
built on top of the work of~\cite{belkin2007convergence}. This is obviously
out of the scope of this contribution.

\label{sec:spherical_harmonics}
\begin{figure*}[!htb]
\centering
\includegraphics[width=0.95\textwidth]{figures/eigenvectors.pdf}
\caption{12 first graph Fourier eigenvectors.}
\label{fig:graph_harmonics}
\end{figure*}

@@

In \figref{gaussian_filters_visualization}, we present three different
ways to plot the graph convolution kernel $K_t(x)=e^{-\tau t x}$. First, they can
be plotted in the graph spectral domain. In this case, we simply evaluate $K_t$
at the graph eigenvalues $\text{diag}(\bLambda)$. Second, we can convolve a
delta on the sphere and plot a gnomonic view of the results. Third, since we are
working on the sphere, we can only plot the section of the convoluted delta. In
\figref{index_section}, we display the selected indexes for the section
plotting. Note that, because of the small irregularities in the HealPix
sampling, the second and the third methods are likely to change depending on the
chosen delta.

>>>>

\subsection{Filter visualization}
\assign{Nathanaël, Tomek, Michaël}
One common visualization for CNN is to display the shape of the learned filters. Since our construction lead to almost (up to the sampling irregularities) spherical filters, we plot in \figref{learned_filter} both the section (on the sphere) and a gnomeview projection on a plane of a random selection of learned filters. The filters are selected from the last layer of the network corresponding the experiment with order $o=2$ for a relative noise level of $2$. Nevertheless, all networks presented similar pattern, at least from a human perspective. The gnomview projection clearly exibits the sampling issue of HealPix. For a detail, on how the filters are plot, please refer to Appendix~\ref{sec:filter_visualization}.
\todo{Tomek: can you say something about the filters.}

@@

\section{Spherical harmonics VS graph Fourier eigenvectors}
\ref{fig:graph_harmonics} displays the first 16 eigenvectors of the
graph Fourier basis used for the convolution. While their is a clear
resemblance with the spherical harmonic, the small irregularities in the
sampling (see \figref{healpix_graph_4}) have an effect on the
graph Fourier eigenvectors. First, conterintuitively, some graph eigenvectors will be
localized~\cite{perraudin2018global}, i.e: they will span only a small subpart
of the sphere.  Second, as Nside increase toward infinity and hence the number
of pixel $n\rightarrow \infty$, we are still unsure if the graph eigenvectors
converge toward the spherical harmonics. We believe that it might be the case
for a different graph construction (fully connected) and that a proof could be
built on top of the work of~\cite{belkin2007convergence}. This is obviously
out of the scope of this contribution.

\label{sec:spherical_harmonics}
\begin{figure*}[!htb]
\centering
\includegraphics[width=0.95\textwidth]{figures/eigenvectors.pdf}
\caption{12 first graph Fourier eigenvectors. Eigenvectors 1-3 could be assotiated to spherical harmonics of order 1, eigenvectors 4-8 to order 2 and 9-15 to order 3. Nevertheless, the graph eigenvectors are only approximating the real spherical harmonics.}
\label{fig:graph_harmonics}
\end{figure*}

@@

In \figref{gaussian_filters_visualization}, we present three different
visualization for the a healpix graph convolution kernel. The kernel used is defined in the graph spectral domain as $K_t(x)=e^{-\tau t x}$. This is the domain used for our first visualization. In this case, we simply evaluate $K_t$
at the graph eigenvalues $\text{diag}(\bLambda)$. The lower eigenvalues $\lambda$ correspond to the lower frequencies, i.e. the spectral mode with less variation. 
As a second visualization, we can observe the kernel directly on the sphere. To do so, we perform the convolution of a
Kroneker on the sphere plot the result with gnomonic projection. Eventually, as we are
working on the sphere with theoretically spherical filters (up the the irregularities of the sampling), we could only plot the section of the convoluted Kroneker. To do so, we convolve a Kroneker on the equator and use the equator for our section as shown in~\figref{index_section}. Note that, because of the small irregularities in the HealPix
sampling, the second and the third methods are subject to small varation depending on the
chosen Kroneker.
